\documentclass[a4paper, 10pt]{article}

\usepackage[utf8x, latin1]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[english]{babel}
\usepackage{fullpage}
\usepackage{multirow}


\begin{document}

\section{Possible laser scanners for robot navigations}
A search on the internet revealed that there was a few sensors which was usually equipped
for robot navigations.

\begin{itemize}
    \item SICK USA LMS-100
    \item SICK USA LMS-200
    \item Hokuyo UTM-30LX
    \item Hokuyo URG-04LX-UG01
    \item Hokuyo URG-04LX
\end{itemize}

The sensors are given in the table below. Included is also the Time-of-Flight camera
SR3000, for comparison.
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
    \hline
    Sensor & Range & Accuracy & FoV & Ang Res & Weight & Scan Freq & Power Cons &  Cost \\
    \hline
    LMS-100 & 20 m & 12 mm &  $270^{\circ}$ & $0.25-0.5^{\circ}$  & 1.1 kg    & 50 Hz & Not specified  & \$5500 \\
    \hline
    LMS-200 & 80 m & 30 mm &  $180^{\circ}$  & $0.25-1^{\circ}$  & 4.5 kg    & 75 Hz & Not specified &  \$5000 \\
    \hline
    UTM-30LX & 30 m & 30 mm & $270^{\circ}$ & $0.25^{\circ}$  & 210 g     & 40 Hz  &$<8$ W   &  \$5000 \\
    \hline
    URG-04LX & 4 m & 10 mm & $240^{\circ}$ & $0.36^{\circ}$ & 160 g  & 10 Hz & ca 2.5 W &  \$2400 \\
    \hline
    URG-04LX-URG01 & 5.6 m & 30 mm & $240^{\circ}$ & $0.36^{\circ}$ & 160 g & 10 Hz & ca 2.5 W & \$1100 \\
    \hline
    SR3000-ToF Camera & 7.5 m & 30 mm & $47.5$ x $ 39.6 ^\circ$ & 176 x 144 & -  & 25
    fps & 18 W max & \$10000 \\
    \hline
\end{tabular}
\end{center}

\section{Data Outputs}
The data output form the Time-of-Flight camera are Cartesian coordinates in $x,y,z$, and
intensity.

The laser scanner sensors Hokuyo URG-04LX and Hokuyo URG-04LX-URG01 samples the circle in 10 bits. 
This means that the angular step size given by 
\begin{equation}
    \phi = \frac{360^\circ}{2^{10}} \approx 0.36^\circ
\end{equation}
The output consists of this sample number and the range which is reported at that sample. 
Since not the full circle is not possible to measure, the step numbers are ranged from 0 to
768, where 0, 384 and 768 implies $-135^\circ$, $0^\circ$ and $135^\circ$ where the front
direction is the reference point. But because of of the field of view of the sensors are
just $240^\circ$ the actual measurable area are from step numbers 44 to 725.


\end{document}
